Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-02 measurements.tex
Starting with the results

\subsubsection{Multicore Network Coding}
\label{subs:multicore-network-coding}

The authors implemented the algorithm described in
Section~\ref{sub:implementation-multicore} on the Raspberry Pi 2 Model B, which
features four ARM Cortex-A7 cores in a Broadcom BCM2836 \ac{SOC} with a 900 MHz
clock. Each core has a 32 KiB L1 data cache and 32 KiB L1 instruction cache. The
cores share a 512 KiB L2 cache. All the measured results, including the baseline
results, were obtained with NEON-enabled code adopted from the FIFI/KODO library
\cite{kodo2011pedersen}. The NEON extension provides an 128-bit \ac{SIMD}
instruction set to the Raspberry Pi 2. Figures~\ref{enc_dec1024},
\ref{enc_dec128} and \ref{enc_dec16} show the encoding and decoding throughput
in MiB per second for different generation sizes ($g$ = 1024, 128, and 16
respectively). The throughput is the rate of generating $g$ coded packets,
divided by the time the encoder took to perform the task. The size of each coded
packet was fixed to $1536$~bytes since that is the typical size of an Ethernet
frame. The blocked operations were performed dividing the matrices in squared
sub-blocks of 16,32,64,...,1024 operands (words in the finite field) in height
and width, and the figures only show the best results (usually block sizes of
16x16 or 32x32 operands since with bigger block sizes, the operands do not fit
in L1 cache).

@@

\paragraph{Baseline encoding} The baseline results involve no recording of the
\ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder uses
only one thread. And the difference between the non-blocked and blocked encoding
schemes is that in the blocked scheme, the matrix multiplications are performed
dividing the matrices in sub-blocks in order to make the algorithm cache
efficient as described in Section~\ref{sub:implementation-multicore}.

\paragraph{Encoding blocked} The encoding results were performed using the
method described in Section~\ref{sub:implementation-multicore}. The time
recorded includes the dependencies resolving, creation of the \ac{DAG}, and the
task scheduling. In practice, it would suffice to calculate and store this
information only once per generation size.

\paragraph{Decoding blocked} The differences between encoding and decoding, is
that the decoding task also involves the matrix inversion. Similarly as with the
encoding results, the time recorded includes the dependencies resolving, the
creation of the \ac{DAG} and the task scheduling. However, to decode, these
calculations are also made for inverting the matrix of coding coefficients.

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
\caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
\label{enc_dec1024}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
\caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
\label{enc_dec128}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
\caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
\label{enc_dec16}
\end{figure}

@@

\paragraph{Comparison of the load of matrix multiplications and inversions}

>>>>

\subsection{Multicore Network Coding}
\label{subs:multicore-network-coding}

The authors implemented the algorithm described in
Section~\ref{sub:implementation-multicore} on the Raspberry Pi 2 Model B,
which features four ARM Cortex-A7 cores in a Broadcom BCM2836 \ac{SOC}
with a 900 MHz clock. Each core has a 32 KiB L1 data cache and 32 KiB
L1 instruction cache. The cores share a 512 KiB L2 cache. All the
measured results, including the baseline results, were obtained with
NEON-enabled code adopted from the Fifi library [\textbf{Fifi reference}].
The NEON extension provides an 128-bit \ac{SIMD} instruction set to the
Raspberry Pi 2. Figures~\ref{enc_dec1024}, \ref{enc_dec128} and
\ref{enc_dec16} show the encoding and decoding throughput in MiB per
second for different generation sizes ($g$ = 1024, 128, and 16
respectively). The throughput is the rate of generating $g$ coded packets,
divided by the time the encoder took to perform the task. The size of
each coded packet was fixed to $1536$~bytes since that is the typical
size of an Ethernet frame. The blocked operations were performed dividing
the matrices in squared sub-blocks of $16,\ 32\ ,\ 64,\ldots,\ 1024$ operands
(words in the finite field) in height and width. The figures show only
block sizes of $16 \times 16$ or $32 \times 32$ operands since with bigger
block sizes, the operands do not fit in L1 cache.

@@

\subsubsection{Baseline encoding}
The baseline results involve no recording of the
\ac{DAG} and are performed in a \emph{by-the-book} fashion. The encoder uses
only one thread. And the difference between the non-blocked and blocked
encoding schemes is that in the blocked scheme, the matrix multiplications are
performed dividing the matrices in sub-blocks in order to make the algorithm
cache efficient as described in Section~\ref{sub:implementation-multicore}.

\subsubsection{Encoding blocked}
The encoding results were performed using the
method described in Section~\ref{sub:implementation-multicore}. The time
recorded includes the dependencies resolving, creation of the \ac{DAG}, and
the task scheduling. In practice, it would suffice to calculate and store this
information only once per generation size.

\subsubsection{Decoding blocked}
The differences between encoding and decoding, is that the decoding task also
involves the matrix inversion. Similarly as with the encoding results, the
time recorded includes the dependencies resolving, the creation of the
\ac{DAG} and the task scheduling. However, to decode, these calculations are also made for inverting the matrix of coding coefficients.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_1024.eps}
\caption{Encoding and Decoding performance for g = 1024 \cite{wunderlich2015network}}
\label{enc_dec1024}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_128.eps}
\caption{Encoding and Decoding performance for g = 128 \cite{wunderlich2015network}}
\label{enc_dec128}
\end{figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{images/2015-04-18_encoding_decoding_16.eps}
\caption{Encoding and Decoding performance for g = 16 \cite{wunderlich2015network}}
\label{enc_dec16}
\end{figure}

@@

\subsubsection{Comparison of the load of matrix multiplications and inversions}
